---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = 'center',
  out.width = "75%"
)
```

# SQUEAK - Statistical Quantification & Understanding of Experimental Animal Kinetics

SQUEAK is a simple package to perform regression modelling and subsequent visualisation of mouse tumour growth data. It is designed to provide accessible access to high quality statistical analysis to support comparisons between groups, while accounting for the inherent variability between individual animals.

This package stands on the shoulders of giants, and wraps a number of excellent other tools that should be given due credit, principally: nlme, ggplot2 and sjPlot.

## Installation

You can install the development version of SQUEAK from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("seedgeorge/SQUEAK")
```

## Minimal Usage Example
The following code uses a dataset included in the package, performs a simple data check, and then makes a simple plot.
```{r example, fig.height=5, fig.width=2.5, message=TRUE, warning=FALSE}
library(SQUEAK)
data("long_mice")
ready_data = check_long(long_mice,
                        timecol = "Days",
                        IDcol = 'Number',
                        groupcol = 'Group',
                        measurementcol = 'Value')
plot_raw_lines(ready_data = ready_data) 
```

In this data, each line represents one mouse, and the mice are grouped in treatment arms.

The next step is to make a mixed-effect regression model, which can also be plotted.
```{r cars, fig.height=3, fig.width=3, message=TRUE, warning=FALSE}
mixed_model = mixed_effect_model(ready_data = ready_data)
plot_modelled_curves(mixed_model)
```
