---
title: "Statistical Quantification & Understanding of Experimental Animal Kinetics (SQUEAK)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SQUEAK}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = " "
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup}
library(SQUEAK)
```

## Test Data
### Real-world long-format data.
This data is a subset of data from a published trial testing several different drugs + a combination. Multiple drug arms, multiple individuals studied longitudinally. An ideal test case for this package. Used with permission of authors: [citation here]
```{r}
data("long_mice")
```

## Data Formats
### Long
The ideal format for this package is 'long', ie. multiple rows per individual/timepoint/group combination
Here are the first ten rows of the long-format test dataset.
```{r}
head(long_mice,n=10)
```
The four columns here are as follows:

 * The day the recording was made
 * The group/drug arm that the individual was part of
 * The ID indicating which individual the result belongs to
 * The measured value - in this case, tumour volume in cm3
 
### Other Formats

We may consider supporting other formats in the future, but at the moment are focusing on other areas. 

## Checking Data

We have included a function that tries to take some of the guess work out of data preparation.
It does a couple of sensible things, including crashing when the data looks 'wrong'.
```{r}
ready_data = check_long(long_mice,
                        timecol = "Days",
                        IDcol = 'Number',
                        groupcol = 'Group',
                        measurementcol = 'Value',
                        reference_level = 'Control')
```

## Basic Plots
It is possible to make some starter plots.
First, we will use a utility function to make a palette that SQUEAK will understand.
```{r fig.height=2, fig.width=4}
colors = set_palette(ready_data)
barplot(rep(1,length(colors)), 
        col=colors, yaxt='n', 
        border=F, 
        names.arg = names(colors), 
        las=2)

# alternatively, you could use a custom named vector, manually assigning a color to each group
colors = c('Control' = 'grey20',
           'DrugX' = '#7570B3',
           'DrugY' = '#D95F02',
           'ComboXY' = '#1B9E77')
barplot(rep(1,length(colors)), 
        col=colors, yaxt='n', 
        border=F, 
        names.arg = names(colors), 
        las=2)
```


A line plot, one line per individual.
```{r fig.height=6, fig.width=4}
# raw line graphs
plot_raw_lines(ready_data = ready_data, palette= colors)
```

Some slopes, one per individual.
```{r fig.height=6, fig.width=4}
# linear model slopes
plot_raw_slopes(ready_data = ready_data, palette = colors)
```

## Model Generation
We will make a regression model using an appropriately named function.
```{r}
mixed_model = mixed_effect_model(ready_data = ready_data,random_slope = T,random_intercept = T)
```


## Model Plotting

```{r fig.height=5, fig.width=5, message=FALSE, warning=FALSE}
plot_modelled_curves(mixed_model,palette= colors,grouptitle = 'Treatment',show_confidence = TRUE)
```

```{r fig.height=4, fig.width=4, message=FALSE, warning=FALSE}
plot_modelled_slopes(model = mixed_model, palette= colors)
```

```{r fig.height=4, fig.width=4, message=FALSE, warning=FALSE}
plot_interaction_forest(mixed_model,palette= colors)
```

## Combined Plot Assembly
```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
slope = plot_raw_lines(ready_data = ready_data, palette= colors)
curvforest = patchwork::wrap_plots(plot_modelled_curves(mixed_model,palette = colors,
                                                        grouptitle = 'Treatment'),
                                   plot_interaction_forest(mixed_model,palette = colors), 
                                                                      ncol=1)
fig = patchwork::wrap_plots(slope, patchwork::plot_spacer(),curvforest, ncol=3,
                            widths = c(2,0.15,2),
                            guides = 'collect')

fig

```

